Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-30 draft/paper1_rachel.tex
Edit stellar mass measurement 2

    In this work, we derive average \m2l{} using the Flexible Stellar Population 
    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model based on the 
    MILES\footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries}
    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a
    \citet{Chabrier2003} IMF between 0.1 to 100 \msun. 
    The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with 
    stochastic star bursts (see Appendix~\ref{app:sed}). 
    This SFH is appropriate for massive galaxies at low redshifts 
    (e.g.\ \citealt{Kauffmann2003}). 
    For stellar metallicity 
    ($[\mathrm{M}/\mathrm{H}]=\log\ \mathrm{Z}/\mathrm{Z}_{\odot}$), we assume a flat 
    distribution between 0.004 to 0.03 (the highest value allowed by FSPS).
    We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
    distribution of $A_{V}$ between 0 to 2 magnitude. 
    The majority of our galaxies are red and quiescent ones so the results are not 
    very sensitive to parameters related to the SFH or the internal dust extinction. 
    To achieve reasonable sampling across these parameters, we generate 250000 models.

    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
    corrected for Galactic extinction. 
    \cmodel{} only accounts for the statistical error on the flux measurement but 
    does not account for systematic uncertainties in the model-fitting process. 
    It therefore underestimates the flux errors of bright galaxies. 
    For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$ and $y$ band 
    (on average, images in $gy$ bands are shallower in depth and/or have higher 
    background noise).  
    Although these are still conservative estimates of the systematic uncertainties 
    involved in the model-fitting, tests using synthetic galaxies show that \cmodel{}
    provides excellent measurements of five-band colors, which are crucial for 
    reliable \m2l{} estimates.
\rachel{I'm a little surprised at the statement that 1\% error is a conservative estimate of systematic uncertainties.  It definitely seems like a conservative estimate of {\em statistical} error.  Can you justify that all systematics are really below 1\%?}
The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$.

>>>>

    In this work, we derive average \m2l{} using the Flexible Stellar Population 
    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model based on the 
    MILES\footnote{http://www.iac.es/proyecto/miles/pages/stellar-libraries}
    (\citealt{MILES1}, \citealt{MILES2}) stellar library and assuming a
    \citet{Chabrier2003} IMF between 0.1 to 100 \msun. 
    The star formation history (SFH) is assumed to follow a delayed-$\tau$ model with 
    stochastic star bursts (see Appendix~\ref{app:sed}). 
    This SFH is appropriate for massive galaxies at low redshifts 
    (e.g.\ \citealt{Kauffmann2003}). 
    For stellar metallicity 
    ($[\mathrm{M}/\mathrm{H}]=\log\ (\mathrm{Z}/\mathrm{Z}_{\odot})$), we assume a 
    flat distribution between 0.004 to 0.03 (the highest value allowed by FSPS).
    We adopt the \citet{Calzetti2000} extinction law with a order two Gamma 
    distribution of $A_{V}$ between 0 to 2 magnitude. 
    The majority of our galaxies are red and quiescent ones so the results are not 
    very sensitive to parameters related to the SFH or the internal dust extinction. 
    To achieve reasonable sampling across these parameters, we generate 250000 
    models.

    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
    corrected for Galactic extinction. 
    Right now, \cmodel{} only accounts for the statistical error on the flux 
    measurement and it certaintly underestimates the true flux errors of bright 
    galaxies.  
    For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$ and $y$ band 
    (on average, images in $gy$ bands are shallower in depth and/or have higher 
    background noise).  
    These empirical \s2n{} choices still only provide lower-limits of the true 
    systematic uncertainties from the model-fitting process. 
    In \citealt{SynPipe}, we evaluate the accuracy of HSC \cmodel{} photometry 
    using synthetic galaxies, and show that \cmodel{} provides excellent measurements 
    of five-band colors, which are crucial for reliable \m2l{} estimates.
    The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$.
